Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-03-02 siip.tex
siip submitted

          \paragraph{A two-day retrospective workshop (\$15K)} at UIUC will wrap up the 
          project. Discussion concerning the process will allow reflection as 
          well as a collection of lessons learned.
          Experiences live testing the developed course material (for example 
          in NPRE412 at UIUC in Fall 2017) will be shared and suggested 
          improvements will be captures as feature requests on GitHub.  The 
          successful parts of the process will be captured a template 
          repository and collaboration instruction manual, intended for use by 
          other groups of faculty seeking to collaborate in a similar way.

>>>>

          \paragraph{A two-day retrospective workshop (\$15K)} at UIUC will wrap up the 
          project. Discussion concerning the process will allow reflection as 
          well as a collection of lessons learned.
          Experiences live testing the developed course material (for example 
          in NPRE412 at UIUC in Fall 2017) will be shared and suggested 
          improvements will be captured as feature requests on GitHub.  
          The process will be captured in a template repository 
          and a collaboration instruction manual will be produced
          for use by other groups of faculty seeking to collaborate in a 
          similar way.
